---
title: "Chapter 3"
subtitle: "Exercises"
author: "Alejandro Ramos Usaj"
date: "5/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bayesrules)
library(tidyverse)
```

# Exercise 3.1

_(Tune your Beta prior: Take I)_ In each situation below, tune a Beta(α,β) model that accurately reflects the given prior information. In many cases, there’s no single “right” answer, but rather multiple “reasonable” answers. 

## a)

Your friend applied to a job and tells you: “I think I have a 40% chance of getting the job, but I’m pretty unsure.” When pressed further, they put their chances between 20% and 60%.

```{r}

```


# Exercise 3.3

_(It’s OK to admit you don’t know)_ You want to specify a Beta prior for a situation in which you have no idea about some parameter $\pi$. You think $\pi$ is equally likely to be anywhere between 0 and 1. Specify and plot the appropriate Beta prior model.

## a.

Specify and plot the appropriate Beta prior model.

```{r}
plot_beta(1, 1)
```

## b.

What is the mean of the Beta prior that you specified? Explain why that does or does not align with having no clue.

```{r}
#alpha/(alpha+beta)
1/2
```

## c.

What is the standard deviation of the Beta prior that you specified?

```{r}
(1*1)/(
  (1+1)^2 * (1+1+1)
)
```

## d.

Specify and plot an example of a Beta prior that has a smaller standard deviation than the one you specified.

```{r}
plot_beta(1.75,1.75)
((1.75)^2)/(
  ((1.75*2)^2) * (1.75 + 1.75 + 1)
)
```


## e.

Specify and plot an example of a Beta prior that has a larger standard deviation than the one you specified.

```{r}
plot_beta(0.75, 0.75)
((0.75)^2)/(
  ((0.75*2)^2) * (0.75 + 0.75 + 1)
)
```


# Exercise 3.4

_(Which Beta? Take I)_ Six Beta pdfs are plotted below. Match each to one of the following models: Beta(0.5,0.5), Beta(1,1), Beta(2,2), Beta(6,6), Beta(6,2), Beta(0.5,6). 

[1,1] = Beta(0.5,0.5)
[2,1] = Beta(1,1)
[1,2] = Beta(2,2)
[1,3] = Beta(6,2)
[2,2] = Beta(0.5,6)
[2,3] = Beta(6,6)

# Exercise 3.5

_(Which Beta? Take II)_ Six Beta pdfs are plotted below. Match each to one of the following models: Beta(1,0.3), Beta(2,1), Beta(3,3), Beta(6,3), Beta(4,2), Beta(5,6). 

[1,1] = Beta(1,0.3)
[1,2] = Beta(3,3)
[1,3] = Beta(4,2)
[2,1] = Beta(2,1)
[2,2] = Beta(5,6)
[2,3] = Beta(6,3)

# Exercise 3.6 

_(Beta properties)_ Examine the properties of the Beta models in Exercise 3.4. 

## a. 

> Which Beta model has the smallest mean? The biggest? Provide visual evidence and calculate the corresponding means.

El modelo Beta(0.5,6) tiene la media mas chica de $\frac{\alpha}{\alpha + \beta}=\frac{0.5}{0.5+6}=0.07$

El modelo Beta(6,2) tiene la media mas grande de $\frac{\alpha}{\alpha + \beta}=\frac{6}{6+2}=0.75$

```{r}
plot_beta(0.5,6, mean = T)
plot_beta(6,2, mean = T)
```


## b. 

> Which Beta model has the smallest mode? The biggest? Provide visual evidence and calculate the corresponding modes.

